### 2020-12-09 manuscript.Rmd
Update github link.

---
#title: "Impact of Nasopharyngeal Specimen Quality of SARS-CoV-2 Test Sensitivity"
#author: "Brendan J. Kelly, MD, MS"
bibliography: bib/references.bib
csl: csl/journal-of-clinical-microbiology.csl
output: html_document
css: style_helvetica_double.css
---

@@

## Title  
Impact of Nasopharyngeal Specimen Quality on SARS-CoV-2 Test Sensitivity

@@

* __Availability of Data__: Data, analysis scripts, and model code are available at github.com/bjklab.

>>>>

---
#title: "Impact of Nasopharyngeal Specimen Quality of SARS-CoV-2 Test Performance"
#author: "Brendan J. Kelly, MD, MS"
bibliography: bib/references.bib
csl: csl/journal-of-clinical-microbiology.csl
output: html_document
css: style_helvetica_double.css
---

@@

## Title  
Impact of Nasopharyngeal Specimen Quality on SARS-CoV-2 Test Performance

@@

* __Availability of Data__: Data, analysis scripts, and model code are available at https://github.com/bjklab/Impact-of-NP-Specimen-Quality-on-SARS-CoV-2-Test-Performance.
